### 2015-01-02 paper_10_intro.tex
lots more references added

One area of research that is focusing on the evaluation of software development organizations
is \textit{software analytics}.  It is less focused on evaluation
and more so on all sorts of analysis of software data.  Early forms of 
software analytics were methods of data mining applied to software engineering data
\cite{Kaner2004,Xie2009,Taylor2010,Halkidi2011}. The term software intelligence was 
used \cite{Hassan2010}, but
the term software analytics has become the common term for referring to the topic \cite{Zhang2011}.
The goal of software analytics is to extract insights
from software artifacts to aide practioners in making better decisions regarding software
development \cite{Zhang2013}.  The main focus areas of software analytics are:
\begin{description}
    \item[User Experience] - How can the software enable the user to more easily or quickly 
        accomplish the task at hand?
    \item[Quality] - How can the number of problems with the software be decreased?
    \item[Development Productivity] - How can the processes or tools be modified to increase 
        the rate at which software is produced? 
\end{description}

@@

>>>>

One area of research that is focusing on the evaluation of software development organizations
is \textit{software analytics}.  It is less focused on evaluation
and more so on all sorts of analysis of software data.  Early forms of 
software analytics were methods of data mining applied to software engineering data
\cite{Kaner2004,Xie2009,Taylor2010,Halkidi2011}. The term software intelligence was 
used \cite{Hassan2010}, but
the term software analytics has become the common term for referring to the topic \cite{Zhang2011}.
The goal of software analytics is to extract insights
from software artifacts to aide practioners in making better decisions regarding software
development \cite{Zhang2013}.  The three main focus areas of software analytics are:
\begin{description}
    \item[User Experience] - How can the software enable the user to more easily or quickly 
        accomplish the task at hand?
    \item[Quality] - How can the number of problems with the software be decreased?
    \item[Development Productivity] - How can the processes or tools be modified to increase 
        the rate at which software is produced? 
\end{description}

@@

%%%%%% a brief outline
the use can be traced back to late 1990s, then techniques of data mining were applied to 
software engineering data

Then it became known as software analytics
desc software analytics

then describe software dev analytics

then describe how all this analysis requires data, so determining the correct data is important \cite{Buse2012}
In order to store the data, tools are needed \cite{Czerwonka2013,Zhang2013} not east to create the right tools \cite{Spraragen2005}

then discuss how gamification is an obvious next step \cite{Dubois2013, Jain2013}

the discuss software quality \cite{Jones2013,Boehm2001,Faizan2012,Miguel2014}
